\SW: II. New lens candidates from the CFHTLS discovered through citizen science

### 2015-04-13 doc/sw-cfhtls.tex

We begin by considering all elliptical galaxies at $z<1$ in our parent
\cfhtls catalog \citep[(XXX confirm with Raphael)]{Gavazzi2014} as
potential lens candidates for the simulated sample. To avoid using a
known lens galaxy for our simulation purpose, we exclude all those
galaxies whose positions match with the lensing galaxies from the SARCS
samples within 2~arcsec.

@@

\begin{figure*}
\begin{center}
\includegraphics[scale=1.3]{sw-cfhtls-figs/lensprop.pdf}
\caption{ \label{fig:lensprop}
Distributions of properties of the lensing galaxies of the simulated
sample compared to the known lens sample SARCS. 
}
\end{center}
\end{figure*}

@@

Indeed, we have found several new lens candidates that were not known
before. In \Fref{fig:isd}, we show the image separation distribution for
the known \rf and \af sample (green), for the \sw identified (known and
new) lens sample (blue) only and combined \cfhtls sample of \rf, \af and
the new \sw lens sample (magenta). It is interesting to note that both
these samples have very similar profiles and thus, the profile of the
combined sample has not changed signficantly. This implies that previous
constraints on the image separation distribution are robust and the \af
selected sample does not suffer from significant incompleteness for
medium to large Einstein radii. This is the regime that probes density
profiles of galaxy groups to clusters.

@@

Finding gravitational lenses is a difficult and complex task. No single
method is perfect. Each method has some advantages over the other. It
may be the case that a single method may never be the best method for
optimising completeness and purity. Visual inspection will likely be
required for pruning candidates at some stage of lens candidate
selection even in the future. Therefore, we would like to understand how
best we should combine the strengths of robots and humans to optimize
the lens finding method.

In this section, we first compare the lens candidates found by
\sw and the lens finding robots and then attempt to understand why each
method failed to detect lenses from the other sample.

@@

In \Fref{fig:zlmgre}, we show the lens redshift and the arc flux
measured in $g$ AB mag as a function of the Einstein radius for the \rf
(green), the \af (red) and the \sw sample (new candidates only in blue
and known candidates as blue circles). We note that the errors on the
redshift measurement should not be too different across the samples
since they are measured by a single method. However, the error on the
total flux of the lensed images are likely to be different across the
samples and the types of systematics are also different.  We have not
attempted to quantify these errors in this work. With that caveat, we
find that the \sw candidates sample is broadly similar to the
robotically found lens candidates in terms of the flux of the lensed
images or the redshift of the lensing galaxies.

@@

The \af, on the other hand, is capable of finding smaller image
separation lenses but a lower limit at $R_{\rm E}=2\arcsec$ was imposed
by the \af team to simplify the selection function of their sample.
Thus, we can compare the \sw and \af samples at about $R_{\rm
E}>2\arcsec$. There is a good overlap between the two samples given that
most of these are candidates and could turn out be not lenses. We again
caution the readers that the uncertainties on the measurements are not
quantified and may change the results to some extent.

The properties considered here do not show any clear differences between
the types of lenses being found by each method. Other properties such as
the flux of the lensing galaxies and the surface brightness of the
lensed images may be useful in showing some qualitative differences but
this is beyond the scope of our current analysis. A more detailed and
accurate analysis is deferred to the future.

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.65]{sw-cfhtls-figs/zl_mg_re.pdf}
\caption{ \label{fig:zlmgre}
Comparison of the lens redshift and the arc magnitude with the
Einstein radius for all of the three lens samples, namely, the \rf (green dots),
\sw (known candidates$-$blue circles and new candidates only$-$blue dots)
and \af (red dots). Alls samples have broadly similar properties.}
\end{center}
\end{figure}

\subsection{Why \sw candidates were missed by lens finding robots?}
We test the \rf and \af on images centered on the new \sw candidates to
trace and understand at what stage the algorithm failed to detect them.

First, we rerun \rf on the new \sw sample. At the beginning, a galaxy
catalog is generated based on magnitude, redshift and SED type
\citep[see]{Gavazzi2014} to select galaxies which are most likely to act
as lenses. We find that about 40\% of the new \sw candidates fail to
meet this initial selection criteria, for example, SW1, SW13, SW19,
SW22, SW26 and SW29.  All of the lensing galaxies are bright enough to
satisfy the magnitude criterion ($i<22$). However, some of them have a
bright companion galaxy, some of them do not look like E/S0 type
galaxies and some are edge on galaxies which could be the reason for
excluding these galaxies from the inital catalog.

@@

In the following steps, the flux from the galaxy is subtracted from the
scaled difference image to enhance the visibility of the faint blue
lensed features. An object finder is run on this image to quantify the
lensed image properties. Another $\sim$~50\% of the \sw candidates could not be
detected by the object finder because properties such as the image area,
axis ratio, magnitude/color and alignment with respect to the lensing
galaxy are not satisfied. Some of the candidates missed at this stage
are, for example, SW4, SW5, SW6, SW25, SW35, SW38 and SW45.

@@

Originally, the \af was run on a large image with an area of $\sim 19350
\times 19350$ pixels$^2$. For the rerun, we work with much smaller
images because this is faster but this alters the measured
noise and hence, affects the number and type of arc detections. We find
that about 30\% of the new candidates are detected without changing any
of the thresholds in the code because of the change in the noise level.
%{\bf does this make sense? - list the IDs of these systems?}

The \af code calculates second order brightness moments around every
pixel to decide if the distribution of flux is elongated in some
direction in order to detect elongated arc-like objects. An elongation
estimator is assigned to every pixel. All pixels with a value of the
elongation stimator above a certain threshold are connected to form the arc
feature. This is called the segmentation of the arc candidate. Subsequently, arc
properties such as the area, mean flux, length and curvature are
determined. We relax the threshold at the segmentation stage and also relax
thresholds mainly on the area of the arc which leads to detection of
about 75\% of the new \sw candidates. We find that relaxing thresholds
on other arc properties does not improve the detection rate significantly
and thus, those thresholds are left unchanged.

Typically, the candidates are missed from the \af sample if a) the arcs
are fainter in $g$ band which is used for arc detection because then the
arc feature is at the noise level and fails detection b) the flux of the
arc and the galaxy are blended in the $g$ band such that the \af
incorrectly connects part of the galaxy to the arc. This results in a
candidate with no morphological characteristics of a typical arc c)
unusually short or thick arcs or d) if the lensed images are almost
circular or point-like which means most of the lensed quasars images
will be missed.

Relaxing the thresholds obviously increases the number of candidate arc
detections but this also includes a large sample of false positives.
For example, the number of arc candidate detections increase by a factor
of $\sim$2 when we relaxed the thresholds in the reruns described above
whereas the number of false positives increase by a factor of $\sim$5.
Thus, it is not recommended to relax these thresholds alone. A better
alternative is to relax the thresholds to increase the completeness and
cross-correlate the arc candidate positions with a galaxy catalog to
discard those candidates which are not close to a putative lensing
galaxy within typical radius in order to reduce the false positives.

@@

\subsection{False negatives: known lenses missed by \sw}
\label{sec:fn}
Like any lens finding method, the \sw system can fail to detect certain
kinds of lenses.  We find that about 40\% of the known sample of lenses
are missed both at \StageOne and II (see \Tref{tab:stats}). In fact, most
of the known lenses from \StageOne are discovered at \StageTwo which
means that the lenses are lost already at \StageOne. Below, we focus on the known
lens sample at \StageOne to understand why some of them are being missed
and possibly find a way to improve the detection rate which can be
adopted in the future \sw lens searches.

@@

For a lens finding method which uses the collective skill, experience and
knowledge of a group of volunteers, it may be difficult to find a single
factor with certainty which causes a lens candidate to be missed. We
attempt to understand whether there is indeed a single dominant factor
that is resulting in the loss of these lenses or the lenses are being
missed due to a combination of multiple reasons. Below, we consider some
of the factors that could affect the efficiency of finding lenses.

\subsubsection{Number of classifications}
First, we check if the number of classifications (Nclass) is
significantly lower for the missed sample compared to the detected one.
Surprisingly, most of the lenses in the known sample have few
classifications (Nclass$<$10) which includes both the detected and
missed lenses. Many of the remaining lenses have between 10 to 20
classifications. And, only a few subjects have Nclass$>$20. They
continue to remain for long in the database because these candidates are
possibly difficult to identify. Overall, we do not find any correlation
for the detected and the missed sample with Nclass.

%{ Let us compare the two samples to see if there are any obvious differences. only 2 out of this sample of 18 were detected at \StageOne (reached high P even with fewer classifications) and missed at \StageTwo (P value was low even after recieving very many classifications). The rest of the 16 lenses were rejected right at \StageOne }
%One of those 6 lenses was detected at \StageOne but failed to get high enough P value at \StageTwo even after receiving a total of 50 classifications (set as the upper limit). The rest of the 5 lenses are already rejected at \StageOne. Upon visual inspection of these 5 systems, they appear to be difficult to identify as lenses because either the lensed images are faint, have low curvature, are close to the edge and/or are not visible due to proximity to an extremely bright galaxy

@@

From the SWAP, the image cutouts inspected by the \sw volunteers receive
a status of detected (if P$>$P$_{\rm acc thresh}$), rejected (if
P$<$P$_{\rm rej thresh}$) and undecided (if P$_{\rm rej thresh}<$ P $<$
P$_{\rm acc thresh}$). In \Fref{fig:comppos}, we compare the positions
of lenses which are detected (red), undecided (green) and rejected
(blue). The left and the right panels have the simulated lens sample and
the known lens candidates sample, respectively. We note that the density
of points do not represent the actual number of detections because, for
cases with large sample size, randomly drawn subsamples are shown for
the ease of visual comparison.

@@

We check how the posterior probability P (see Paper I for the
mathematical definition) of an image or a subject to contain a lens
changes as the image receives more classifications from multiple
volunteers. A graphical representation of changing probabilities for
increasing classifications is called a trajectory plot. In
\Fref{fig:detmis}, we show the trajectory plots of a few examples of
detected lenses (top left panels) and missed lenses (bottom left panels)
from \StageOne of \sw. The number of classifications (Nclass) for a
subject increase from top to bottom.  Also, every subject is assigned a
prior probability P0$=2\times10^{-4}$ (grey dashed line) and starts at
the middle of the trajectory plot. The P value of a subject is updated
with every classification from the volunteer.  If a volunteer identifies
a lens candidate, the trajectory moves to the right otherwise moves to
the left. A subject is accepted if it crosses the blue-dashed line
marking the (P$_{\rm acc thresh}=0.95$) on the right and is rejected, if
it crosses the red-dashed line marking the P$_{\rm rej thresh}=10^{-7}$
on the left.

@@

For a quantitative comparison of the large and small kicks for the
entire samples of detected and missed known lenses, we show a plot of
histogram on the right of \Fref{fig:detmis}. Qualitatively, there are
four types of volunteers making classifications - those causing positive
large kicks (correct classifications by high power volunteers, those
causing positive small kicks (correct classifications by low power
volunteers), those causing negative small kicks (incorrect
classifications by low power volunteers) and those causing negative
large kicks (incorrect classifications by high power volunteers). The
four histograms in the figure correspond to these four types of
volunteers for each sample (that is, detected or missed). The kick size
is small if $\Delta$ log(P)$=$log (P$_{\rm current}) - $log(P$_{\rm
previous}) < \Delta$log(P)$_{\rm cut}$ (chosen as 1.2) and is large
if greather than $\Delta$log(P)$_{\rm cut}$.

Some of the key differences are i) the ratio of positive large kicks to
positive small kicks for the detected sample is higher than the missed
sample suggesting that the fraction of high power volunteers is large
for the detected sample ii) in terms of Nclass, the missed sample is
dominated by volunteers causing negative small kicks whereas for the
detected sample there is a comparable contribution from three types of
volunteers - positive small and large kicks and negative small kicks.
iii) the Nclass from volunteers with negative large kicks are lower, both
for the detected and the missed samples. This is consistent with our
expectation that high power volunteers should not be making incorrect
classifications. Therefore, lack of high power volunteers classifying
the missed lenses seems to be one of the major factors.

We rerun SWAP for \StageOne where we use classifications from volunteers
who produce $\Delta$ log(P)$>1.2$ only. This obviously means reducing
the total Nclass per subject by a large fraction. As a result, we also
need to change the P$_{\rm acc thresh}$ which is chosen to be 0.1 and we
find that about a third of the missed lenses are detected while all the
previously detected lenses remain detected too. The others simply do not
have enough classifications from volunteers producing large positive
kicks. Thus, it may be possible to detect more promising candidates if
we preferentially show the rejected systems to a few high power
volunteers. We understand that changing the rejection and acceptance
thresholds will likely increase the rate of FPs along with improved
completeness. After testing on a subsample of both \StageOne and
\StageOne FPs, we find that a small fraction of FPs are rejected when
only classifications with $\Delta$ log(P)$>1.2$ only are considered.
Therefore, we think it is worth adopting the new strategy in the future
runs of SWAP in future lens searches.

@@

The bottom panels show the missed or rejected lenses. The green (and red)
trajectories show visually easier (and more difficult) to identify
lenses. In spite of some mild qualitative differences, both set of
trajectories have very similar behaviour. The trajectories in panel e
are typical of this sample in terms of Nclass and the dominance of short
negative kicks. The panel f represents a small fraction of this sample
where the kicks are only short and negative. The panel g shows how some
lenses receive a bunch of large positive kicks which are led to
rejection by still mostly negative short kicks. Finally, panel h shows
those cases of lenses which received almost sufficient number of large
positive kicks to be detected but ended up being rejected.

The top panels show the detected lenses. The cases shown with green trajectories
in each panel can be thought of counterparts of the trajectories of the missed
lenses in the corresponding bottom panels except that the type of volunteers are
different. Most detected lenses are similar to the case in panel a which are
detected within a few classifications but coming from large positive kicks.
Panel b represents a few odd cases which are dominated mainly by short positive
kicks. Panel c shows a lens getting more classifications because of the tug
between positive and negative kicks whereas the panel d represents the extreme
cases when the images are on the verge of being rejected but are saved thanks
to a series of large positive kicks. The red trajectories are some more
examples of randomly selected cases which demonstrate how having sufficient
number of large positive kicks allows lenses to be detected in spite of several
short negative kicks.

@@

As described in the appendix of \PaperOne, the posterior probability $P$
of a subject is determined by the $P_{\rm L}$ and $P_{\rm D}$ of all the
volunteers who clicked on the subject, via Bayes' Theorem. Each agent
will apply a ``kick'' of a different size to the subject probability,
$\Delta\log(P)$, which can be either positive (if the classifier thinks
the subject contains a lens) or negative (if the classifier thinks the
subject does not contain a lens). For instance, given a subject
(not) containing a lens, a volunteer with high ($P_{\rm D}$) $P_{\rm L}$
implies a large (negative) positive kick irrespective the value of
($P_{\rm L}$) $P_{\rm D}$ as shown in the (right most) middle panel of
\Fref{fig:skilldlnp}. However, large (negative) positive kicks are
still possible for a volunteer located in the (lower) upper triangle
with different combinations of ($P_{\rm L}$, $P_{\rm D}$) suggesting that
the kick is not a simple function of ($P_{\rm L}$, $P_{\rm D}$).

@@

\begin{figure*}
\begin{center}
\includegraphics[scale=1.0]{sw-cfhtls-figs/dlnp_skill.pdf}
\caption{ \label{fig:skilldlnp}
Skill of the volunteers and $\Delta\log(P)$ given a lens or not a lens in
an image as a function of $P_{\rm L}$ and $P_{\rm D}$. These
quantities indicate the ability of the volunteers but do not have a simple
linear relation with $P_{\rm L}$ and $P_{\rm D}$.  
\question{AM}{PJM, should we just use power everywhere instead of the
$\Delta\log(P)$? This figure and this section still needs to be
polished. }
}
\end{center}
\end{figure*}

>>>>

We begin by considering all elliptical galaxies at $z<1$ in our parent
\cfhtls catalog \citep[(XXX confirm with Raphael)]{Gavazzi2014} as
potential lens candidates for the simulated sample. To avoid using a
known lens galaxy for our simulation purpose, we exclude all those
galaxies whose positions match with the lensing galaxies from the SARCS
samples within 2~arcsec (XXX check).

@@

\begin{figure*}
\begin{center}
\includegraphics[scale=1.3]{sw-cfhtls-figs/lensprop.pdf}
\caption{ \label{fig:lensprop}
Distributions of properties of the lensing galaxies of the simulated
sample compared to the known lens sample SARCS. %(XXXX confirm what's being plotted? which band - i?)
}
\end{center}
\end{figure*}

@@

Indeed, we have found several new lens candidates that were not known
before. In \Fref{fig:isd}, we show the image separation distribution for
the known \rf and \af sample (green), for the \sw identified (known and
new) lens sample (blue) only and combined \cfhtls sample of \rf, \af and
the new \sw lens sample (magenta). It is interesting to note that both
these samples have very similar profiles and thus, the profile of the
combined sample has not changed signficantly. This implies that previous
constraints on the image separation distribution are robust and the \af
selected sample does not suffer from significant incompleteness for
medium to large Einstein radii. This is the regime that probes density
profiles of galaxy groups to clusters.
%%{\bf AM: understand what Phil wanted to say about AF's (in)completeness}

@@

Finding gravitational lenses is a difficult and complex task. No one
method is perfect. Each method has some advantages over the other. It
may be the case that a single method may never be the best method for
optimising completeness and purity. Visual inspection will likely be
required for pruning candidates at some stage of lens candidate
selection even in the future. Therefore, we would like to understand how
best we should combine the strengths of robots and humans to optimize
the lens finding method.

In this section, we first compare the lens candidates found by
\sw and the lens finding robots and then attemp to understand why each
method failed to detect lenses from the other sample.

@@

In \Fref{fig:zlmgre}, we show the lens redshift and the arc flux
measured in $g$ AB mag as a function of the Einstein radius for the \rf
(green), the \af (red) and the \sw sample (new candidates only in blue
and known candidates as black circles). We note that the errors on the
redshift measurement should not be too different across the samples
since they are measured by a single method. However, the error on the
total flux of the lensed images are likely to be different across the
samples and the types of systematics are also different.  We have not
attempted to quantify these errors in this work. With that caveat, we
find that the \sw candidates sample is broadly similar to the
robotically found lens candidates in terms of the flux of the lensed
images or the redshift of the lensing galaxies.

@@

The \af, on the other hand, is capable of finding smaller image
separation lenses but a lower limit on $R_{\rm E}$ was imposed by the
\af team to simplify the selection function of their sample. Thus, we
can compare the \sw and \af samples at about $R_{\rm E}>2\arcsec$. There
is a good overlap between the two samples given that most of these are
candidates and could turn out be not lenses. We again caution the
readers that the uncertainties on the measurements are not quantified
and may change the results to some extent.

The properties considered here do not show any clear differences between
the types of lenses being found by each method. Other properties such as
the flux of the lensing galaxies and the surface brightness of the
lensed images may be useful in showing some qualitative differences but
this is beyond the scope of our current analysis. A more detailed and
accurate analysis is deferred to the future.
%{\bf check out of the 55 promising \af how many are missed by \sw ?}

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.65]{sw-cfhtls-figs/zl_mg_re.pdf}
\caption{ \label{fig:zlmgre}
Comparison of the lens redshift and the arc magnitude with the
Einstein radius for all of the three lens samples, namely, the \rf (green dots),
\sw (known candidates$-$black circles and new candidates only$-$blue dots)
and \af (red dots). Alls samples have broadly similar properties.}
\end{center}
\end{figure}

\subsection{Why \sw candidates were missed by lens finding robots?}
We rerun the \rf and \af on images centered on the new \sw candidates to
trace and understand at what stage the algorithm failed to detect them.

First, we rerun \rf on the new \sw sample. At the beginning, a galaxy
catalog is generated based on magnitude, redshift and SED type
\citep[see]{Gavazzi2014} to select galaxies which are most likely to act
as lenses. We find that about 40\% of the new \sw candidates fail to
meet this initial selection criteria, for example, SW1, SW13, SW19, SW22, SW26
and SW29.  All of the lensing galaxies are bright enough to satisfy the
$i<22$ criterion. However, some of them have a bright companion galaxy,
some of them do not look like E/S0 type galaxies and some are edge on
galaxies.

@@

In the following steps, the flux from the galaxy is subtracted from the
scaled difference image to enhance the visibility of the faint blue
lensed features. An object finder is run on this image to quantify the
lensed image properties. About 50\% of the \sw candidates could not be
detected by the object finder because properties such as the image area,
axis ratio, magnitude/color and alignment with respect to the lensing
galaxy are not satisfied. Some of the candidates missed at this stage
are, for example, SW4, SW5, SW6, SW25, SW35, SW38 and SW45.

@@

Originally, the \af was run on a large image with an area of $\sim 19350
\times 19350$ pixels$^2$. For the rerun, we work with much smaller
images because this is faster but this alters the measured
noise and hence, affects the number and type of arc detections. We find
that about 30\% of the new candidates are detected without changing any
of the thresholds in the code because of the change in the noise level.
%{\bf does this make sense?}

The \af code calculates second order brightness moments around every
pixel to decide if the distribution of flux is elongated in some
direction in order to detect elongated arc-like objects. An elongation
estimator is assigned to every pixel. All pixels with a value of the
elongation stimator above a certain threshold are connected to form the arc
feature. This is building of the arc candidate. Subsequently, arc
properties such as the area, mean flux, length and curvature are
determined. We relax the threshold at the building stage and also relax
thresholds mainly on the area of the arc which leads to detection of
about 75\% of the new \sw candidates. We find that relaxing thresholds
on other arc properties do not improve the detection rate significantly
and thus are left unchanged.

Typically, the candidates are missed from the \af sample if a) they are
brighter in the redder band rather than the bluer $g$ band used for arc
detection because then the arc feature will be at the noise level and
will fail detection b) the flux of the arc and the galaxy are
blended in the $g$ band such that the \af mistakenly connects part of the
galaxy to the pixels belonging to the arc candidate which then results in a
candidate with no morphological characteristics of an arc or c) if the
candidate is not elongated which means most of the lensed quasars with
circular looking lensed images will be missed.

Relaxing the thresholds obviously increases the total number of
candidate detections which includes a large sample of false positives.
For example, the number of arc candidate detections increase by a factor
of $\sim$2 when we relaxed the thresholds in the reruns described above
whereas the number of false positives increase by a factor of $\sim$5.
Thus, it is not recommended to relax these thresholds alone. A better
alternative is to relax the thresholds to increase the completeness and
cross-correlate the arc candidate positions with a galaxy catalog to
discard those candidates which are not close to a putative lensing
galaxy within typical radius in order to reduce the false positives.

@@

\subsection{False negatives: known lenses missed by \sw}
\label{sec:fn}
Like any lens finding method, the \sw system can fail to detect certain
kinds of lenses.  We find that about 40\% of the known sample of lenses
are missed both at \StageOne and II (see \Tref{tab:stats}). In fact, most
of the known lenses from \StageOne are discovered at \StageTwo suggesting
that most lenses are lost right at \StageOne. Below, we focus on the known
lens sample at \StageOne to understand why some of them are being missed
and possibly find a way to improve the detection rate which can be
adopted in the future \sw lens searches.

@@

For a lens finding method which uses collective skill, experience and
knowledge of a group of volunteers, it may be difficult to find a single
factor with certainty which causes a lens candidate to be missed. We
attempt to understand whether there is indeed a single dominant factor
that is resulting in the loss of these lenses or the lenses are being
missed due to a combination of multiple reasons. Below, we consider some
of the factors that could affect the efficiency of finding lenses.

\subsubsection{Number of classifications}
First, we check if the number of classifications (Nclass) is
significantly lower for the missed sample compared to the detected one.
Surprisingly, most of the lenses in the known sample have few
classifications (Nclass$<$10) which includes both the detected and
missed lenses. Many of the remaining lenses have between 10 to 20
classifications. And, only a few subjects have Nclass$>$20. They
continue to remain for long in the database because these candidates are
possibly difficult to identify. Therefore, the distribution of Nclass
can not be the reason for losing the lenses from the missed sample.

%{ Let us compare the two samples to see if there are any obvious differences. only 2 out of this sample of 18 were detected at \StageOne (reached high P even with fewer classifications) and missed at \StageTwo (P value was low even after recieving very many classifications). The rest of the 16 lenses were rejected right at \StageOne XXX}
%One of those 6 lenses was detected at \StageOne but failed to get high enough P value at \StageTwo even after receiving a total of 50 classifications (set as the upper limit). The rest of the 5 lenses are already rejected at \StageOne. Upon visual inspection of these 5 systems, they appear to be difficult to identify as lenses because either the lensed images are faint, have low curvature, are close to the edge and/or are not visible due to proximity to an extremely bright galaxy

@@

From the SWAP, the image cutouts inspected by the \sw volunteers receive
a status of detected (if P$>$P$_{\rm acc thresh}$), rejected (if
P$<$P$_{\rm rej thresh}$) and undecided (if P$_{\rm rej thresh}<$ P $<$
P$_{\rm acc thresh}$). In \Fref{fig:comppos}, we compare the positions
of lenses which are detected (red), undecided (green) and rejected
(blue). The left and the right panels have the simulated lens sample and
the known lens candidates sample, respectively. We note that the density
of points do not represent the actual number of detections because, for some
cases, randomly selected subsamples are shown for the ease of visual
comparison.

@@

We check how the posterior probability P (see Paper I for the
mathematical definition) of an image or a subject to contain a lens
changes as the image receives more classifications from multiple
volunteers.  In \Fref{fig:detmis}, we show the trajectory plots of a few
examples of detected lenses (top left panels) and missed lenses (bottom
left panels) by \sw at \StageOne. The number of classifications (Nclass)
for a subject increase from top to bottom.  Also, every subject is
assigned a prior probability P0$=2\times10^{-4}$ (grey dashed line) and
starts at the middle of the trajectory plot. The P value of a subject is
updated with every classification from the volunteer.  If a volunteer
identifies a lens candidate, the trajectory moves to the right otherwise
moves to the left. A subject is accepted if it crosses the blue-dashed
line marking the (P$_{\rm acc thresh}=0.95$) on the right and is
rejected, if it crosses the red-dashed line marking the P$_{\rm rej
thresh}=10^{-7}$ on the left.

@@

For a quantitative comparison of the large and small kicks for the
entire samples of detected and missed known lenses, we show a plot of
histogram on the right of \Fref{fig:detmis}. Qualitatively, there are
four types of volunteers making classifications - those causing positive
large kicks (correct classifications by high power volunteers, those
causing positive small kicks (correct classifications by low power
volunteers), those causing negative small kicks (incorrect
classifications by low power volunteers) and those causing negative
large kicks (incorrect classifications by high power volunteers). The
four histograms in the figure correspond to these four types of
volunteers for each sample (that is, detected or missed). The kick size
is small if $\Delta$ log(P)$=$log (P$_{\rm current}) - $log(P$_{\rm
previous}) < \Delta$log(P)$_{\rm cut}$ (chosen to be 1.2) and is large
if greather than $\Delta$log(P)$_{\rm cut}$.

Some of the key differences are i) the ratio of positive large kicks to
positive small kicks for the detected sample is higher than the missed
sample suggesting that the fraction of high power volunteers is large
for the detected sample ii) in terms of Nclass, the missed sample is
dominated by volunteers causing negative small kicks whereas for the
detected sample there is a comparable contribution from three types of
volunteers - positive small and large kicks and negative small kicks.
iii) the Nclass from volunteers with negative large kicks are lower both
for the detected and the missed samples. this is consistent with our
expectation that high power volunteers should not be making incorrect
classifications.Therefore, lack of high power volunteers classifying
the missed lenses seems to be one of the major factors.

We rerun SWAP for \StageOne where we use classifications from volunteers
who produce $\Delta$ log(P)$>1.2$ only. This obviously means reducing
the total Nclass per subject by a large fraction. As a result, we also
need to change the P$_{\rm acc thresh}$ which is chosen to be 0.1 and we
find that about a third of the missed lenses are detected while all the
previously detected lenses remain detected too. The others simply do not
have enough classifications from volunteers producing large positive
kicks. Thus, it may be possible to detect more promising candidates if
we preferentially show the rejected systems to a few high power
volunteers. We understand that changing the rejection and acceptance
thresholds will likely increase the rate of FPs along with
improved completeness but most probably the increase in FPs will not be
too significant and that it will still be worth using the new strategy.

@@

The bottom panels show the missed or rejected lenses. The green (and red)
trajectories show visually easier (and more difficult) to identify
lenses. In spite of some mild qualitative differences, both set of
trajectories have very similar behaviour. The trajectories in panel e
are typical of this sample in terms of Nclass and the dominance of short
negative kicks. The panel f represents a small fraction of this sample
where the kics are only short and negative. The panel g shows how some
lenses receive a bunch of large positive kicks which are led to
rejection by still mostly negative short kicks. Finally, panel h shows
those cases of lenses which received almost sufficient number of large
positive kicks to be detected but ended up being rejected.

The top panels show the detected lenses. The cases shown with green trajectories
in each panel can be thought of counterparts of the trajectories of the missed
lenses in the corresponding bottom panel except that the type of volunteers are
different. Most detected lenses are similar to the case in panel a which are
detected within a few classifications but coming from large positive kicks.
Panel b represents a few odd cases which are dominated mainly by short positive
kicks. Panel c shows a lens getting more classifications because of the tug
between positive and negative kicks whereas the panel d represents the extreme
cases when the images are on the verge of being rejected but are saved thanks
to a series of large positive kicks. The red trajectories are some more
examples of randomly selected cases which demonstrate how having sufficient
number of large positive kicks allows lenses to be detected in spite of several
short negative kicks.

@@

As described in the appendix of \PaperOne, the posterior probability $P$
of a subject is determined by the $P_{\rm L}$ and $P_{\rm D}$ of all the
volunteers who clicked on the subject, via Bayes' Theorem. Each agent
will apply a ``kick'' of a different size to the subject probability,
$\Delta\log(P)$, which can be either positive (if the classifier thinks
the subject contains a lens) or negative (if the classifier thinks the
subject does not contain a lens). For instance, given a subject
(not) containing a lens, a volunteer with high ($P_{\rm D}$) $P_{\rm L}$
implies a large (negative) positive kick irrespective the value of
($P_{\rm L}$) $P_{\rm D}$ as shown in the (right most) middle panel of
\Fref{fig:skilldlnp}. However, large (negative) positive kicks are
still possible for a volunteer located in the (lower) upper triangle
with different combinations of ($P_{\rm L}$,$P_{\rm D}$) suggesting that
the kick is not a simple function of ($P_{\rm L}$,$P_{\rm D}$).

@@

\begin{figure*}
\begin{center}
\includegraphics[scale=1.0]{sw-cfhtls-figs/dlnp_skill.pdf}
\caption{ \label{fig:skilldlnp}
Skill of the volunteers, $\Delta\log(P)$ given a lens or not a lens in
an image as a function of $P_{\rm L}$ and $P_{\rm D}$. Each of these
quantities represent ability of the Volunteers but do not have a simple
linear relation with $P_{\rm L}$ and $P_{\rm D}$.  
\question{AM}{PJM, should we just use power everywhere instead of the
$\Delta\log(P)$? This figure and this section still needs to be
polished.}
}
\end{center}
\end{figure*}
